Pillar 1 - Sequential Pattern Mining

### 2019-03-13 Pillar 1 - Sequential Pattern Mining.Rmd
simplify code of make_sequence and use purrr to compute several types of sequences

    pull(list_item) %>%

    as("transactions")

@@

## Sequences
```{r making sequences, cache = TRUE}
make_sequence <- function(data = d_transactions$taken_PF_HL, item = item){

  data_temp <- data %>%
    arrange(
      sequenceID,
      eventID
    ) %>%
    filter(
      !is.na(eventID) # exclude courses that were never taken.
      ) %>%

    group_by(
      sequenceID,
      eventID
    ) %>%
    summarise(
      list_item = list(unique(!!enquo(item)))
    ) %>%
    ungroup

  sequences <- data_temp %>%
    pull(
      list_item
      ) %>%
    as("transactions")

  # indicate sequence ID and event ID for each transaction
  sequences@itemsetInfo <- data_temp %>%
    select(
      sequenceID,
      eventID
      ) %>%
    as.data.frame

@@

#
# Making sequences
sequences <- list()

sequences$taken <- make_sequence(item = item   )
sequences$PF    <- make_sequence(item = item_PF)
sequences$HL    <- make_sequence(item = item_HL)
sequences$G     <- make_sequence(data = d_transactions$G    , item = item_G  )

#inspect(head(sequences$G, 10))
```

>>>>

    pull(list_item) %>%
    as("transactions")

@@

## Sequences
```{r making sequences, cache = TRUE}
make_sequence <- function(data, item){

  data_temp <- data %>%

    filter(!is.na(eventID)) %>%  # exclude courses that were never taken.

    arrange(sequenceID, eventID) %>%
    group_by(sequenceID, eventID) %>%
    summarise(list_item = list(unique(!!enquo(item)))) %>%
    ungroup

  # extract transactions
  sequences <- data_temp %>% pull(list_item) %>% as("transactions")

  # add attributes fro sequence ID and event ID
  sequences@itemsetInfo <- data_temp %>% select(sequenceID, eventID) %>% as.data.frame

@@

sequences <- tribble(
  ~ ID   ,  ~ data                    , ~ item,
  "taken", d_transactions$taken_PF_HL, quo(item),
  "PF"   , d_transactions$taken_PF_HL, quo(item_PF),
  "HL"   , d_transactions$taken_PF_HL, quo(item_HL),
  "G"    , d_transactions$G          , quo(item_g)
  ) %>%

  mutate(sequences = list(data, item) %>% pmap(make_sequence))

inspect(head(sequences$sequences[[2]], 10))
```
